A Bias-Variance Decomposition of Information Transfer in Multi-Task Learning

### 2020-08-17 arxiv/proof_examples.tex
pf

With \eqref{simple1} and Lemma \ref{prop_model_shift_tight}, we can prove Proposition \ref{prop_dist_transition}, which gives a transition threshold with respect to the ratio between the model bias and the noise level. With slight abuse of notations, we shall write $\hat a_i$ and $\hat b_k$ as $a_i$ and $b_k$ throughout the proof.

\begin{proof}[Proof of Proposition \ref{prop_dist_transition}]
	In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$. Then solving equations \eqref{eq_a12extra} and \eqref{eq_a34extra} with $\lambda_i=1$, we get that
	\begin{align}
		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
	\end{align}
	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_2^{\MTL}$ to $\hat{\beta}_2^{\STL}$ as 
\be\label{Deltavar}
\begin{split}
\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \\
&=\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
\end{split}
\ee
with high probability, where 
	\begin{align*}
		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.
	\end{align*}
	%where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
	Next for the model shift bias
	$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
	we can get from Lemma \ref{prop_model_shift_tight} (or rather its proof) that
\be\label{Deltabeta} 
\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_{\bias}}{ \Delta_{\bias}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
	where 
	$$\Delta_{\bias}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2}  \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$	
%\begin{align*}
%		\Delta_{\bias} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
%		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}d^2}
%	\end{align*}
%	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\bias}$ as
%	\be\label{Deltabeta} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\bias} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{p^{1/2+\e}d^2} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4. \ee	
%	Hence we obtain that
%	\begin{align*}
%		\frac{1 + a_3 + a_4}{(a_1 + a_2)^2}
%		= \frac{(c_1 + c_2)^3}{(c_1 + c_2 - 1)^3} + \bigo{p^{-1/2+\varepsilon}}.
%	\end{align*}
Note that 
 \be\label{var-beta}\te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} .\ee
Then we can track its sign using \eqref{Deltavar} and \eqref{Deltabeta}.

\noindent{\bf Positive transfer.} With \eqref{Deltavar} and \eqref{Deltabeta}, we conclude that if
\be\label{upper101}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_+^2(\rho_1) +  \oo(1) \right) < \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
	we have that $\delta_{\vari} > \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$. We can simplify \eqref{upper101} to
	\be\label{pos1}  \frac{pd^2}{\sigma^2}  <   \Phi(\rho_1, \rho_2)\cdot \left( \al_+^2(\rho_1) +  \oo(1) \right)^{-1}, \ee
Since $ \Psi(\beta_1,\beta_2)=pd^2/\sigma^2$ and $\nu\ge \al_+^2(\rho_1) +  \oo(1) $, it gives the first statement of Proposition \ref{prop_dist_transition}.

\noindent{\bf Negative transfer.} On the other hand, if
\be\label{upper102}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right) > \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
	we have that $\delta_{\vari} < \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$. We can simplify \eqref{upper102} to
	\be\label{neg1} \Psi(\beta_1,\beta_2)=\frac{ p d^2}{\sigma^2}  >  \Phi(\rho_1, \rho_2) \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1}, \ee
which gives the second statement of Proposition \ref{prop_dist_transition}.
\end{proof}

@@

\begin{proof}[Proof of Proposition \ref{prop_var_transition}]
In the setting of Proposition \ref{prop_var_transition}, the test loss is given by \eqref{eq_te_mtl_2task}. 
%the validation loss and the test error become
%\begin{align*}
%		\val(\hat{B}; w_1, w_2)
%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)} \nonumber \\
%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)}, 
%\end{align*}
%and 
%where $\hat v=\hat{w_1}/\hat{w_2}$ is the global minimizer of $\val(\hat{B}; w_1, w_2)$. 
In the isotropic model, using again the concentration result, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_2^{\MTL})$ as
\begin{align*}
	\te(\hat{\beta}_2^{\MTL}) &=~ \hat{v}^2 \left[d^2 +\left( \hat v-1\right)^2\kappa^2\right]\bigtr{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2} \cdot \left(1+\OO(p^{-1/2+\e})\right)\nonumber \\
	& + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2)  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} \hat v^2X_1^\top X_1}
\end{align*}
with high probability for any constant $\e>0$.

In the current setting, we can also show that  \eqref{hatv_add1}  holds for $\hat v$. 
Since the proof is almost the same as the one for Lemma \ref{lem_hat_v}, we omit the details. 
%$$|\hat w-1|=\OO(p^{-1}).$$
%as in \eqref{hatw_add1}. 
%We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}. 
Thus under the choice of parameters in \eqref{choiceofpara}, $\te(\hat{\beta}_2^{\MTL}) $ can be simplified as in \eqref{simple1}: 
\be \label{simple2}
\begin{split}
\te(\hat{\beta}_2^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \\ 
&+(1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \\
&+(1+\OO(n^{-\e}))\cdot (\sigma_1^2-\sigma_2^2)  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
\end{split}
\ee
Then we have 
$$ \te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} - \delta_{\vari}^{(2)},$$
where 
$$\delta_{\vari}:=\sigma_2^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }$$
satisfies \eqref{Deltavar} with $\sigma^2$ replaced by $\sigma_2^2$, 
$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]$$
satisfies \eqref{Deltabeta}, and $\delta_{\vari}^{(2)}$ is defined as
\begin{align*}	
	\delta_{\vari}^{(2)}:=(1+\OO(n^{-\e}))\cdot (\sigma_1^2 -\sigma_2^2) \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
\end{align*}
%$$	\te(\hat{\beta}_t^{\MTL}) = \left[\Delta_{\bias} + \Delta_{diff}+  \sigma_2^2 \cdot \tr(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \right]\cdot \left(1+\OO(p^{-1/2})\right), $$
%where $\Delta_{\bias}:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has 
To estimate this new term $\delta_{\vari}^{(2)}$, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to some error using \eqref{eq_isometric}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$. This process leads to the following estimates on $\delta_{\vari}^{(2)}$:
\be\label{Deltavar2} 
\al_-(\rho_1) - \oo(1)  \le  {\delta_{\vari}^{(2)}}/{ \Delta_{\vari}^{(2)}} \le \al_+(\rho_1) +  \oo(1) , \ee
where 
$$ \Delta_{\vari}^{(2)}:=(\sigma_1^2 -\sigma_2^2) \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3}.$$
Next we compare $\delta_{\vari}$ with $\delta_{\bias} + \delta_{\vari}^{(2)}$. Our main focus is to see how the extra $\delta_{\vari}^{(2)}$ affects the information transfer in this case.

@@

Note that the condition $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$ for $\rho_1 > 40$ gives that $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}. Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\bias}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$.  It remains to consider the case $\sigma_1^2 \ge \sigma_2^2$.

>>>>

With \eqref{simple1} and Lemma \ref{prop_model_shift_tight}, we can prove Proposition \ref{prop_dist_transition}, which gives a transition threshold with respect to the ratio between the model bias and the noise level. %With slight abuse of notations, we shall write $\hat a_i$ and $\hat b_k$ as $a_i$ and $b_k$ throughout the proof.

\begin{proof}[Proof of Proposition \ref{prop_dist_transition}]
	In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$. Then solving equations \eqref{eq_a12extra} and \eqref{eq_a34extra} with $\lambda_i\equiv 1$, we get that
	\begin{align}
		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
	\end{align}
	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_2^{\MTL}$ to $\hat{\beta}_2^{\STL}$ as 
\be\label{Deltavar}
\begin{split}
\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } =\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
\end{split}
\ee
with high probability, where 
	\begin{align*}
		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.
	\end{align*}
	%where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
	Next for the model shift bias
	$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
	we can get from Lemma \ref{prop_model_shift_tight} that
\be\label{Deltabeta} 
\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_{\bias}}{ \Delta_{\bias}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
	where 
	$$\Delta_{\bias}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2}  \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$	
%\begin{align*}
%		\Delta_{\bias} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
%		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}d^2}
%	\end{align*}
%	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\bias}$ as
%	\be\label{Deltabeta} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\bias} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{p^{1/2+\e}d^2} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4. \ee	
%	Hence we obtain that
%	\begin{align*}
%		\frac{1 + a_3 + a_4}{(a_1 + a_2)^2}
%		= \frac{(c_1 + c_2)^3}{(c_1 + c_2 - 1)^3} + \bigo{p^{-1/2+\varepsilon}}.
%	\end{align*}
Note that by \eqref{simple1}, we have
 \be\label{var-beta}\te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} .\ee
Then we can track its sign using \eqref{Deltavar} and \eqref{Deltabeta}.

\vspace{5pt}

\noindent{\bf Positive transfer.} With \eqref{Deltavar} and \eqref{Deltabeta}, we conclude that if
\be\label{upper101}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_+^2(\rho_1) +  \oo(1) \right) < \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
then $\delta_{\vari} > \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$. We can simplify \eqref{upper101} to
	\be\label{pos1}  \frac{pd^2}{\sigma^2}  <   \Phi(\rho_1, \rho_2)\cdot \left( \al_+^2(\rho_1) +  \oo(1) \right)^{-1}, \ee
Since $ \Psi(\beta_1,\beta_2)=pd^2/\sigma^2$ and $\nu\ge \al_+^2(\rho_1) +  \oo(1) $, it gives the first statement of Proposition \ref{prop_dist_transition}.

 \vspace{5pt}

\noindent{\bf Negative transfer.} On the other hand, if
\be\label{upper102}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right) > \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
	we have that $\delta_{\vari} < \delta_{\bias}$, which implies $\te(\hat{\beta}_2^{\MTL})>\te(\hat{\beta}_2^{\STL})$. We can simplify \eqref{upper102} to
	\be\label{neg1} \frac{ p d^2}{\sigma^2}  >  \Phi(\rho_1, \rho_2) \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1}, \ee
which gives the second statement of Proposition \ref{prop_dist_transition}.
\end{proof}

@@

\begin{proof}[Proof of Proposition \ref{prop_var_transition}]
In the setting of Proposition \ref{prop_var_transition}, the test loss is given by \eqref{eq_te_mtl_2task}. 
%the validation loss and the test error become
%\begin{align*}
%		\val(\hat{B}; w_1, w_2)
%	&=  n_1 \cdot \bignorm{\Sigma_1^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_2^{\top}X_2\left (\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
%		&+ n_1 \sigma^2 \cdot \frac{w_1^2}{w_2^2} \bigtr{\left(\frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)} \nonumber \\
%		&+ n_2 \cdot \frac{w_1^2}{w_2^2}\bignorm{\Sigma_2^{1/2}\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}X_1^{\top}X_1\left(\beta_s - \frac{w_1}{w_2}\beta_t\right)}^2 \nonumber \\
%		&+ n_2 \sigma^2 \cdot \bigtr{\left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-2} \left(\sigma_1^2 \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + \sigma_2^2  X_2^{\top}X_2\right)}, 
%\end{align*}
%and 
%where $\hat v=\hat{w_1}/\hat{w_2}$ is the global minimizer of $\val(\hat{B}; w_1, w_2)$. 
For the isotropic model, using again the concentration result, Lemma \ref{largedeviation}, we can rewrite $\te(\hat{\beta}_2^{\MTL})$ as
\begin{align*}
	\te(\hat{\beta}_2^{\MTL}) &=~ \hat{v}^2 \left[d^2 +\left( \hat v-1\right)^2\kappa^2\right]\bigtr{ (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2} \cdot \left(1+\OO(p^{-1/2+\e})\right)\nonumber \\
	& + \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } + (\sigma_1^2 -\sigma_2^2)  \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} \hat v^2X_1^\top X_1}
\end{align*}
with high probability for any constant $\e>0$.

In the current setting, we can also show that  \eqref{hatv_add1}  holds for $\hat v$. 
Since the proof is almost the same as the one for Claim \ref{lem_hat_v}, we omit the details. 
%$$|\hat w-1|=\OO(p^{-1}).$$
%as in \eqref{hatw_add1}. 
%We omit the details of the proof, since it is almost the same as the one in the proof of Lemma \ref{lem_hat_v}. 
Thus under \eqref{choiceofpara}, $\te(\hat{\beta}_2^{\MTL}) $ can be simplified as in \eqref{simple1}: 
\be \label{simple2}
\begin{split}
\te(\hat{\beta}_2^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \\ 
&+(1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \\
&+(1+\OO(n^{-\e}))\cdot (\sigma_1^2-\sigma_2^2)  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-2} X_1^\top X_1} ,
\end{split}
\ee
with high probability for some small constant $\e>0$. Then we can write
$$ \te(\hat{\beta}_2^{\STL})-\te(\hat{\beta}_2^{\MTL}) =\delta_{\vari} - \delta_{\bias} - \delta_{\vari}^{(2)},$$
where 
$$\delta_{\vari}:=\sigma_2^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma_2^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }$$
satisfies \eqref{Deltavar} with $\sigma^2$ replaced by $\sigma_2^2$; 
$$\delta_{\bias}:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]$$
satisfies \eqref{Deltabeta}; $\delta_{\vari}^{(2)}$ is defined as
\begin{align*}	
	\delta_{\vari}^{(2)}:=(1+\OO(n^{-\e}))\cdot (\sigma_1^2 -\sigma_2^2) \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_1^\top X_1} .
\end{align*}
%$$	\te(\hat{\beta}_t^{\MTL}) = \left[\Delta_{\bias} + \Delta_{diff}+  \sigma_2^2 \cdot \tr(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \right]\cdot \left(1+\OO(p^{-1/2})\right), $$
%where $\Delta_{\bias}:= \sigma_2^2 \cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} }$ has 
To estimate this new term $\delta_{\vari}^{(2)}$, we use the same arguments as in the proof of Lemma \ref{prop_model_shift_tight}: we first replace $X_1^\top X_1$ with $n_1\id$ up to a small error using \eqref{eq_isometric}, and then apply Lemma \ref{lem_cov_derivative} to calcualte $\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-2}}$. This process leads to the following estimates on $\delta_{\vari}^{(2)}$:
\be\label{Deltavar2} 
\al_-(\rho_1) - \oo(1)  \le  \frac{\delta_{\vari}^{(2)}}{ \Delta_{\vari}^{(2)}} \le \al_+(\rho_1) +  \oo(1) , \ee
where 
$$ \Delta_{\vari}^{(2)}:=(\sigma_1^2 -\sigma_2^2) \frac{\rho_1 (\rho_1+\rho_2)}{(\rho_1+\rho_2-1)^3}.$$
Next we compare $\delta_{\vari}$ with $\delta_{\bias} + \delta_{\vari}^{(2)}$. Our main focus is to see how the extra $\delta_{\vari}^{(2)}$ affects the information transfer in this case.

@@

{\cor(start here)} Note that the condition $\ex{\norm{\beta_1 - \beta_2}^2}< \frac{1}{2} {\sigma_2^2}  \cdot \Phi(\rho_1, \rho_2)$ for $\rho_1 > 40$ gives that $\delta_{\vari}>\delta_{\bias} $ by Proposition \ref{prop_dist_transition}. Hence if $\sigma_1^2\le \sigma_2^2$, then $\delta_{\vari}^{(2)}<0$ and we always have $\delta_{\vari} > \delta_{\bias}+ \delta_{\vari}^{(2)}$, which gives $\te(\hat{\beta}_2^{\MTL})<\te(\hat{\beta}_2^{\STL})$.  It remains to consider the case $\sigma_1^2 \ge \sigma_2^2$.
